### 2020-06-22 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
fix institute name

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{hyperref}
%\usepackage{academicons}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Optimization Letters}
%
\begin{document}

@@

\institute{               
V. Gergel \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{gergel@unn.ru} 
\and
E. Kozinov \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{evgeny.kozinov@itmm.unn.ru} 
\and
K. Barkalov \at
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{konstantin.barkalov@itmm.unn.ru}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}

%\usepackage{hyperref}
%\usepackage{academicons}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Optimization Letters}
%
\begin{document}

@@

\institute{               
Victor Gergel \at
%\at Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{gergel@unn.ru} 
\and
Evgeniy Kozinov \at
%\at Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{evgeny.kozinov@itmm.unn.ru} 
\and
Konstantin Barkalov \at
%\at Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
\email{konstantin.barkalov@itmm.unn.ru} \\
\at Institute of Informational Technologies, Mathematics and Mechanics, Mathematical Center, Lobachevsky State University of Nizhni Novgorod, Gagarin ave., 23, Nizhni Novgorod, Russia 
}
